---
title: 'SDS 237: Final Project Checkpoint 6 - Peopling the Data'
author:
  - Fill
  - Fill
  - Fill
  - Fill
date: 09/30/2021
output: 
  rmdformats::readthedown:
    df_print: paged
editor_options: 
  chunk_output_type: inline
---

## Purpose and Instructions

This checkpoint is adapted from an experimental ethnographic methods exercise designed by my Ph.D. advisor Kim Fortun (UCI, Anthropology). She called it "peopling a project." The goal will be to draw to the surface the (typically invisible) human labor behind this dataset. Complete parts 1-3 below. Part 4 is optional. Commit your code often, and be sure to push all changes to GitHub.com when you're finished. 

## Part 1: List relevant social groups

To start, create a long list of people that are implicated in the production, aggregation, or circulation of this dataset. List those people below.

1. 
2. 
3. 
4. 
...

## Part 2: Map social forces

Copy your list of stakeholders into the center column of the table below. (Add more rows if necessary, by copying a blank row and pasting it below.) In the left column, list social forces that *enable* people to engage in the production, aggregation, or circulation of this data. Examples of social forces include things like: social institutions, cultural norms, education, economics, laws, politics, technology, discourse, language, etc. In the right column, list social forces that *corrode* people's ability to engage in the production, aggregation, or circulation of this data. Some social forces may appear in both columns. The goal of this section is to understand the social force fields the data is situated within. 

| Catalysts.             | Social Groups.             | Corrosions.             |
|------------------------|----------------------------|-------------------------|
|                        |                            |                         |
|                        |                            |                         |
|                        |                            |                         |
|                        |                            |                         |
|                        |                            |                         |
|                        |                            |                         |
|                        |                            |                         |
|                        |                            |                         |
|                        |                            |                         |
|                        |                            |                         |


## Part 3: Profile a social group

Select at least **two** listed social groups. Profile each group below by answering some combination of the following questions. As you are thinking about your responses to these questions refer back to the social forces chart. Consider how social forces both enable and corrode their abilities to engage with the data in the ways they do. Each write-up below should be at least 200 words. 

* How are their bodies implicated in the production of the data? What senses do they engage in their work with the data? What kinds of movements and exertions must they make in relation to the data?
* What do their day-to-day jobs look like or entail?
* What kind of education or training do they have?
* What interest do they have in the data or incentives to report the data in a particular way?
* What kind of critical judgment calls must they make when producing, aggregating, or circulating the data? 
* How is the work and standpoints of these social groups valued or validated?
* What social norms or discourses guide how they engage with the data?
* What protocols or regulations are they required to abide by?
* How do people in this social group identify themselves?
* What is the demographic make-up of the social group?

I encourage you not to make assumptions about a particular social group, but to search for relevant literature, media, or data pertaining to this social group. To enrich this section of the document, you may find YouTube videos of these individuals at work or speaking at a conference or with a news anchor. Feel free to embed those in the Markdown. Alternatively, you might find training guides or protocols directed at these social groups. Or maybe you'll track down Glassdoor profiles that depict information about their jobs. You might also check out data published by the [Bureau of Labor Statistics](https://www.bls.gov/oes/current/oes_stru.htm#17-0000) about typical compensation for these jobs broken down by demographic indicators. Be sure to cite all sources.

### Social group 1:


### Social group 2:


### Social group 3 (optional):


### Social group 4 (optional):


## Part 4: Bonus! This section is optional. 

Select a few variables in the dataset where we can see traces of the humans that collected or aggregated the data. (Note that we could make a case that there are traces of the human in all of the variables, but let's just focus on ones more relevant.) Import and clean your data and find a way to creatively visualize the human traces in that variable. 

```{r}
#library(tidyverse)
#Import here
#Clean here
```

```{r}
#Visualize here
```

